This thesis is separated in five parts. The introduction deals with the
motivation of the examined approach, the related work and preliminaries
introducing concepts of probability theory and notations regarding finite and
infinite words. The follwing, second, chapter recalls known results of the
theory of infinite words and associated word automata. Additionally, we discuss
the less colloquial concepts of probabilistic automata for infinite words. In
the next chapter we present results of the theory of automata on infinite
trees. Notably, we introduce and use the concept of alternation and present its
close connection with graph games. The rest of the chapter is dedicated to the
introduction of \aclp*{WDTA} and the examination of basic results of the
associated theory and the possibilities to model other probabilistic systems.
The fourth chapter deals with the synthesis problem associated with
specifications which can be described as $\omega$-regular languages and those
which are described in terms of probabilistic word automata. Both probabilistic
and antagonistic environments are considered. The last chapter contains a
conclusion which includes an evaluation of the results and a discussion of
ideas for further research.

To the best of our knowledge this thesis achieves to contribute genuine new
results for the synthesis problem where the specification is expressed as
almost-surely accepting \acl*{PBA}. Namely, we solve the strategy synthesis for
such specifications for \aclp*{POMDP} and for antagonistic environments in
Theorem \ref{thm:pbastratpomdpsynthesis} and Theorem \ref{thm:pbasynthesis}
respectively. These results are inspired by the concepts of \aclp*{WDTA} which
are also a contribution of this thesis. For all our arguments we are committed
to transparently illustrate the origin of used arguments by selectively
presenting proofs of known results.
